The Effect of Episodic Retrieval on Inhibition in Task Switching

### 2015-11-26 2015/Episodic Retrieval & Inhibition/Manuscript Files/main.tex
finalised manuscript; added Bayesian est.

%%%--------------------------------------------------------------------------------------------
\documentclass[a4paper, doc, natbib]{apa6}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes} 
\usepackage{etoolbox}

@@

\title{The Effect of Episodic Retrieval on Inhibition in Task Switching}
\shorttitle{Episodic Retrieval \& Inhibition}
\author{James A. Grange, Agnieszka Kowalczyk, and Rory O'Loughlin}
\affiliation{School of Psychology, Keele University, UK}

\note{{\bf Word Count:} 2,890 (Main body, not including abstract or references.)}
% \note{{\bf Under Review---Please, no direct quotes.}}

@@

\authornote{Please address correspondence to James A. Grange, School of Psychology, Dorothy Hodgkin Building, Keele University, Keele, UK, ST5 5BG. Email: grange.jim@gmail.com. All raw data and analysis code are available to download at http://bit.ly/1l22EUV.}

\leftheader{Grange}

\abstract{Inhibition in task switching is inferred from n--2 task repetition costs: the observation that ABA task switching sequences are responded to slower than CBA sequences. This is thought to reflect the persisting inhibition of task A, which slows re-activation attempts. \cite{Mayr2002} reported an experiment testing a critical non-inhibitory account of this effect, namely episodic retrieval: If the trial parameters for task A match across an ABA sequence, responses should be facilitated due to priming from episodic retrieval; a cost would occur if trial parameters mismatch. In a rule-switching paradigm, Mayr reported no significant difference in n--2 repetition cost when the trial parameters repeated or switched across an ABA sequence, in contrast to the episodic retrieval account. Here we provide a replication of the critical aspects of Mayr's design. Using Bayesian analysis to quantify evidence for or against a null hypothesis, we find evidence for reduced n--2 repetition costs when trial parameters repeat compared to when they switch. In contrast to Mayr's conclusion, we suggest that episodic retrieval can influence the measure of inhibition in task switching, although it cannot explain it entirely.}

@@

%----------------------
\section{Introduction}

Stimuli in the human environment typically afford more than one action. Sat at a computer, for example, there are many tasks that could be performed, such as writing a manuscript, checking the weather, or playing a game of online chess. In order to act in a goal-directed manner, humans must be able to \emph{select} the relevant task (writing a paper) in the face of competing tasks (playing chess), and maintain this task in an active state so that it can dominate behaviour. However, such \emph{stable} representations must also be \emph{flexible}, so that they can be removed when the goals change (such as when the phone rings). This tension between the need for stability and flexibility of task representations has been called the \emph{stability--flexibility dilemma} \citep{Goschke2000}.

How the cognitive system addresses the stability--flexibility dilemma has been studied using the task switching paradigm \citep{Grange2014a,Kiesel2010,Vandierendonck2010}, wherein participants have to make speeded responses to simple cognitive tasks. For example, participants might be presented with number stimuli, and be asked to switch between judging whether the stimulus is odd/even or lower/higher than five. One cognitive process thought to be essential for task switching performance is the active inhibition of competing tasks. Evidence for inhibition comes from the so-called backward inhibition paradigm \citep{Koch2010, Mayr2000}, where participants are required to switch between three tasks (A, B, and C). 
It is a consistent finding that ABA task switching sequences are performed slower and with less accuracy than CBA sequences. This \emph{n--2 repetition cost} is thought to reflect the persisting inhibition of task A in an ABA sequence, which hinders its re-activation in the last trial of the triplet.

The n--2 repetition costs is important as it appears to be robust against non-inhibitory explanations which have successfully accounted for other ``inhibitory'' phenomena \citep{Mayr2007}. One potential explanation---episodic retrieval \citep{Neill1997}---was explored by \cite{Mayr2002}. This theory suggests (adapted to a task switching context) that when a task has been performed an episodic trace of trial parameters (such as the cue, stimulus characteristics, and the response made) is stored in memory. When this task is cued again, retrieval of the most recent episodic trace occurs. If the parameters of the presented trial differ from that of the retrieved episode (e.g., a different response is required), a mismatch cost occurs relative to if the retrieved episode matches parameters of the current trial (which will prime performance). Thus, according to this account, n--2 repetition costs reflect a mismatch cost, as trial parameters typically differ between both instances of task A in an ABA sequence.

@@

\cite{Mayr2002} found no statistically significant interaction between n--2 task repetitions and n--2 response repetition [$F$(1, 38) = 1.3, $p$ = .26]; that is, there was no significant difference between n--2 task repetition costs for n--2 response repetitions and n--2 response switches. Mayr suggested this provided evidence against the episodic retrieval account of n--2 task repetition costs, and instead favours the inhibitory account.

@@

\subsection{Participants}
All participants were recruited via the participant panel run by the School of Psychology at Keele University. All participants were first year undergraduates participating in exchange for partial course credit. Our final sample comprised 76 participants. Three additional participants were removed before analysis due to failure to maintain accuracy levels above 90\%.

@@

\subsection{Apparatus \& Stimuli}
Stimuli were presented on a 17in. monitor connected to a PC running E-Prime v. 2.0 software. The stimulus display consisted of an 8cm by 8cm square frame. A black circle (diameter = 1cm) served as the trial stimulus. Possible cues were the words ``horizontal'', ``vertical'', or ``diagonal'', and were presented in black font (enter font details here) directly above the stimulus frame. Responses were collected via a 1-ms precise USB keyboard.

\subsection{Procedure}
On each trial a cue was presented above the frame for 150ms. After this time, the circle stimulus appeared in one of the four corners of the frame. The cue remained on the screen during stimulus presentation. The task required participants to mentally make a spatial transformation of the stimulus' location according to the rule dictated by the task cue, and to make a spatially-congruent response to this translated location. For example, if the stimulus was in the top-right corner, the participant would need to make a top-left response if the task was ``horizontal'', a bottom-right response if the task was ``vertical'', and a bottom-left response if the task was ``diagonal''. Responses were made on the numerical part of the keyboard, using the ``4'', ``5'', ``1'', and ``2'' keys for top-left, top-right, bottom-left, and bottom-right responses respectively. Participants were asked to respond as quickly and as accurately as possible. Once a response was registered, the frame was cleared for a response--cue interval of 150ms, after which time a new cue appeared for the next trial. The cue for the next trial was chosen randomly with the constraint that task repetitions could not occur (cf., Mayr, 2002); the stimulus location was chosen randomly with no constraints on each trial. If participants made an error, the word ``Error!'' appeared in red for xxms above the stimulus frame (in the cue's position).

Participants were presented with 16 trials as practice (which could be repeated upon request). The main experiment presented 4 blocks of 120 trials.

@@

%----------------------
\section{Results}
Participants who failed to maintain session-wise accuracy above 90\% were immediately discarded from analysis. For response time analysis, the first two trials from each block were removed, as were error trials and the two trials following an error. Response times were trimmed by removing all RTs faster than 150ms, as well as any RTs slower than 2.5 standard deviations above the mean for each participant for each cell of the experimental design. Mean RTs and error rates can be seen in Table \ref{tab:behaviouralData}.

@@

\subsection{Response Times}
Response times were analysed via a two factor repeated measures analysis of variance (ANOVA) with the factors as described in \emph{Design}. There was a significant main effect of \emph{Sequence}, with slower RTs to ABA sequences (1,025ms) than to CBA sequences (958ms), $F$(1, 75) = 94.14, $p$<.001, $\eta_g^2$ = .018. The Bayes factor for this main effect was $BF_{10}$ = 1e+12, which provides substantial support for the presence of n--2 repetition costs. There was also a significant main effect of \emph{Response Sequence}, with faster RTs to response repetitions (976ms) than to response switches (1,007ms), $F$(1, 75) = 18.21, $p$<.001, $\eta_g^2$ = .004. The Bayes factor for this main effect was $BF_{10}$ = 338.77, which again provides substantial support for the alternative hypothesis. Critically, there was a significant interaction of both factors, $F$(1, 75) = 9.60, $p$<.01, $\eta_g^2$ = .001. The n--2 repetition cost was 48ms for response repetitions [t(75) = 4.2, $p$<.001] and 86ms for response switches [t(75) = 13.0, $p$<.001].

The progression of the Sequential Bayes Factor for the interaction is shown in Figure \ref{fig:bayesFactor}. We stopped data collection after 76 participants, as at this point the criteria for our stopping rule had been reached\footnote{We could have stopped after 75 participants, but the last two participants were tested in successive sessions, so the Bayes factor was not checked until after the final participant.}. The final Bayes Factor for the difference of n--2 repetition costs for response repetitions and response switches was $BF_{10}$ = 9.974, which suggests that the alternative hypothesis is about 10 times more likely given than the data, which provides strong support that n--2 repetition costs are influenced by response repetitions.

\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/bayesFactor.pdf}
\caption{Progression of the Sequential Bayes Factor [expressed as log($BF_{10}$)] as sample size increased. The criteria for a priori stopping rules are shown as dotted horizontal lines.}
\label{fig:bayesFactor}
\end{center}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/recruitmentOrder.pdf}
\caption{Simulated progression of the Sequential Bayes Factors for a random set of 50 different recruitment orders for the current data set. See text for details.}
\label{fig:recruitmentOrder}
\end{center}
\end{figure}

\subsection{Accuracy}
Accuracy analysis showed no significant effect of task sequence [$F$(1, 75) = 3.36, $p$=.07, $\eta_g^2$ = .006]; the Bayes factor for this main effect was $BF_{10}$ = 0.618, which provides only anecdotal support for the null. The main effect of response repetition was significant [$F$(1, 75) = 12.17, $p$<.001, $\eta_g^2$ = .019], suggestive of better accuracy for response repetitions (96.28\%) than for response switches (95.41\%). The Bayes factor was $BF_{10}$ = 29.66, which provides substantial support for the alternative. The interaction was not significant [$F$(1, 75) = 1.32, $p$=.25, $\eta_g^2$ = .003]; the Bayes factor was $BF_{10}$ = 0.238, which provides moderate support for the null hypothesis.

@@

For clarification, note that we have not provided evidence that episodic retrieval can explain the n--2 task repetition cost entirely, but rather it reduces the cost. Indeed, the n--2 task repetition cost was still statistically significant even when the trial parameters matched across n--2 task repetitions [i.e., n--2 response repetitions; \emph{t}(75) = 4.20, $p$<.001; $BF_{10}$ = 286.50]. Therefore, our findings do not provide evidence against the inhibitory explanation of these costs. Rather, we have shown that these costs can be reduced with successful episodic retrieval. As such, researchers should be cognisant of the potential contribution of episodic retrieval mismatches inflating estimates of n--2 task repetition costs when wishing to use this effect for measuring inhibition.

Our results differ to those reported by \cite{Mayr2002}. We suggest that our modifications to Mayr's original design improved the sensitivity of the paradigm to be able to detect potential episodic retrieval effects on n--2 task repetitions. The modifications were made to enhance the magnitude of n--2 task repetition costs, so that modulation of this cost with response repetitions could be more easily detected. Specifically, removing the possibility of n--2 task repetitions likely enhanced the n--2 task repetition cost as it has been shown that allowing immediate repetitions reduces this cost \citep{Philipp2006}. We also used the shortest RCI used by Mayr (150ms), as it is a consistent finding that this increases the n--2 repetition cost \cite{Gade2005, Grange2009, Mayr2000, Mayr2002}. Any one of these modifications could explain the difference in results between this study and that of Mayr (2002). Future research should aim to examine the potential role for episodic retrieval influencing n--2 task repetition costs by providing further replications to this study \citep{OpenScienceCollaboration2015}.

>>>>

%%%--------------------------------------------------------------------------------------------
\documentclass[a4paper, man, natbib]{apa6}
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes} 
\usepackage{etoolbox}

@@

\title{The Effect of Episodic Retrieval on Inhibition in Task Switching}
\shorttitle{Episodic Retrieval \& Inhibition}
\author{James A. Grange, Agnieszka W. Kowalczyk, and Rory O'Loughlin}
\affiliation{School of Psychology, Keele University, UK}

\note{{\bf Word Count:} 3,124 (Main body, not including abstract or references.)}
% \note{{\bf Under Review---Please, no direct quotes.}}

@@

\authornote{Please address correspondence to James A. Grange, School of Psychology, Dorothy Hodgkin Building, Keele University, Keele, UK, ST5 5BG. Email: grange.jim@gmail.com. All raw data and analysis code are available to download at http://bit.ly/1OgH9v0.}

\leftheader{Grange, Kowalczyk, \& O'Loughlin}

\abstract{Inhibition in task switching is inferred from n--2 task repetition costs: the observation that AB$A$ task switching sequences are responded to slower than CB$A$ sequences. This is thought to reflect the persisting inhibition of task A, which slows re-activation attempts. \cite{Mayr2002} reported an experiment testing a critical non-inhibitory account of this effect, namely episodic retrieval: If the trial parameters for task A match across an ABA sequence, responses should be facilitated due to priming from episodic retrieval; a cost would occur if trial parameters mismatch. In a rule-switching paradigm, Mayr reported no significant difference in n--2 repetition cost when the trial parameters repeated or switched across an ABA sequence, in contrast to the episodic retrieval account. Here we provide a replication of the critical aspects of Mayr's design. Using Bayesian analysis to quantify evidence for or against a null hypothesis, we find evidence for reduced n--2 repetition costs when trial parameters repeat compared to when they switch. In contrast to Mayr's conclusion, we suggest that episodic retrieval can influence the measure of inhibition in task switching, although it cannot explain it entirely.}

@@

%----------------------
Stimuli in the human environment typically afford more than one action. Sat at a computer, for example, there are many tasks that could be performed, such as writing a manuscript, checking the weather, or playing a game of online chess. In order to act in a goal-directed manner, humans must be able to \emph{select} the relevant task (writing a paper) in the face of competing tasks (playing chess), and maintain this task in an active state so that it can be performed. However, such \emph{stable} task representations must also be \emph{flexible}, so that they can be removed when the goals change (such as when the phone rings). This tension between the need for stability and flexibility of task representations has been called the \emph{stability--flexibility dilemma} \citep{Goschke2000}.

How the cognitive system addresses the stability--flexibility dilemma has been studied using the task switching paradigm \citep{Grange2014a,Kiesel2010,Vandierendonck2010}, wherein participants have to make speeded responses to simple cognitive tasks. For example, participants might be presented with number stimuli, and be asked to switch between judging whether the stimulus is odd/even or lower/higher than five. One cognitive process thought to be essential for task switching performance is the inhibition of competing tasks. Evidence for inhibition comes from the so-called backward inhibition paradigm \citep{Koch2010, Mayr2000}, where participants are required to switch between three tasks (A, B, and C).  It is a consistent finding that AB$A$ task switching sequences are performed slower and with less accuracy than CB$A$ sequences. This \emph{n--2 repetition cost} is thought to reflect the persisting inhibition of task A in an ABA sequence, which hinders its re-activation in the last trial of the triplet.

The n--2 repetition cost is important as it appears to be robust against non-inhibitory explanations \citep{Mayr2007}. One potential explanation of the n--2 repetition cost that does not assume inhibition---the episodic retrieval account \citep{Neill1997}---was explored by \cite{Mayr2002}. This theory suggests (adapted to a task switching context) that when a task has been performed an episodic trace of trial parameters (such as the cue, stimulus characteristics, and the response made) is stored in memory. When this task is cued again, retrieval of the most recent episodic trace occurs. If the parameters of the presented trial differ from that of the retrieved episode (e.g., a different response is required), a mismatch cost occurs relative to if the retrieved episode matches parameters of the current trial (which will prime performance). Thus, according to this account, n--2 repetition costs reflect a mismatch cost, as trial parameters typically differ between both instances of task A in an ABA sequence.

@@

\cite{Mayr2002} found no statistically significant interaction between n--2 task repetition and n--2 response repetition [$F$(1, 38) = 1.3, $p$ = .26]; that is, there was no significant difference between n--2 task repetition costs for n--2 response repetitions and n--2 response switches. Mayr suggested this provided evidence against the episodic retrieval account of n--2 task repetition costs, and instead favours the inhibitory account.

@@

\subsection{Participants}
All participants were undergraduates at the School of Psychology at Keele University. Participants took part in exchange for partial course credit or a small cash payment (£6). Our final sample comprised 76 participants. Three additional participants were removed before analysis due to failure to maintain accuracy levels above 90\%.

@@

\subsection{Apparatus \& Stimuli}
Stimuli were presented on a 17in. monitor connected to a PC running E-Prime v. 2.0 software. The stimulus display consisted of an 8cm by 8cm square frame. A black circle (diameter = 1cm) served as the trial stimulus. Possible cues were the words ``horizontal'', ``vertical'', or ``diagonal'', and were presented in size 22 black Verdanna font directly above the stimulus frame. Responses were collected via a 1-ms precise USB keyboard.

\subsection{Procedure}
On each trial a cue was presented above the frame for 150ms. After this time, the circle stimulus appeared in one of the four corners of the frame. The cue remained on the screen during stimulus presentation. The task required participants to mentally make a spatial transformation of the stimulus' location according to the rule dictated by the task cue, and to make a spatially-congruent response to this translated location. For example, if the stimulus was in the top-right corner of the frame, the participant would need to make a top-left response if the task was ``horizontal'', a bottom-right response if the task was ``vertical'', and a bottom-left response if the task was ``diagonal''. Responses were made on the numerical part of the keyboard, using the ``4'', ``5'', ``1'', and ``2'' keys for top-left, top-right, bottom-left, and bottom-right responses respectively. Participants were asked to respond as quickly and as accurately as possible. Once a response was registered, the frame was cleared for a response--cue interval of 150ms, after which time a new cue appeared for the next trial. The cue for the next trial was chosen randomly with the constraint that task repetitions could not occur (cf., Mayr, 2002); the stimulus location was chosen randomly with no constraints on each trial. If participants made an error, the word ``Error!'' appeared in red for 1000ms above the stimulus frame (in the cue's position).

Participants were presented with 16 trials as practice. The practice block was repeated once if the participant made more than four errors. The main experiment presented 4 blocks of 120 trials.

@@

%----------------------
\section{Results}
For response time analysis, the first two trials from each block were removed, as were error trials and the two trials following an error. Response times were trimmed by removing all RTs faster than 150ms, as well as any RTs slower than 2.5 standard deviations above the mean for each participant for each cell of the experimental design. Mean RTs and error rates can be seen in Table \ref{tab:behaviouralData}.

@@

\subsection{Response Times}
Response times were analysed via a two factor repeated measures analysis of variance (ANOVA) with the factors as described in \emph{Design}. There was a significant main effect of \emph{Sequence}, with slower RTs to ABA sequences (1,025ms) than to CBA sequences (958ms), $F$(1, 75) = 94.14, $p$<.001, $\eta_G^2$ = .018. The Bayes factor for this main effect was $BF_{10}$ = 1e+12, which provides substantial support for the presence of n--2 repetition costs. There was also a significant main effect of \emph{Response Sequence}, with faster RTs to response repetitions (976ms) than to response switches (1,007ms), $F$(1, 75) = 18.21, $p$<.001, $\eta_G^2$ = .004. The Bayes factor for this main effect was $BF_{10}$ = 338.77, which again provides substantial support for the alternative hypothesis. Critically, there was a significant interaction of both factors, $F$(1, 75) = 9.60, $p$<.01, $\eta_G^2$ = .001. The n--2 repetition cost was 48ms for response repetitions [$t$(75) = 4.2, $p$<.001; $BF_{10}$ = 271.24] and 86ms for response switches [$t$(75) = 13.0, $p$<.001; $BF_{10}$ = 7.11e+17].

The progression of the Sequential Bayes Factor for the interaction is shown in Figure \ref{fig:bayesFactor}. We stopped data collection after 76 participants, as at this point the criteria for our stopping rule had been reached\footnote{We could have stopped after 75 participants, but the last two participants were tested in successive sessions, so the Bayes factor was not checked until after the final participant.}. The final Bayes Factor for the difference of n--2 repetition costs for response repetitions and response switches was $BF_{10}$ = 9.97, which suggests that the alternative hypothesis is about 10 times more likely given than the data, which provides strong support that n--2 repetition costs are influenced by response repetitions.

\begin{figure*}
\begin{center}
\includegraphics[width = \textwidth]{Images/bayesFactor.pdf}
\caption{Progression of the Sequential Bayes Factor [expressed as log($BF_{10}$)] as sample size increased. The criteria for a priori stopping rules are shown as dotted horizontal lines.}
\label{fig:bayesFactor}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width =\textwidth]{Images/recruitmentOrder.pdf}
\caption{Simulated progression of the Sequential Bayes Factors for a random set of 50 different recruitment orders for the current data set. See text for details.}
\label{fig:recruitmentOrder}
\end{center}
\end{figure*}

\subsubsection{Bayesian Parameter Estimation}
We wished to supplement our Bayes factor analysis with Bayesian parameter estimation of the mean and effect size of the difference in n--2 task repetition cost between response repetitions and response switches. As such, we used the (default) methods outlined by \cite{Kruschke2013}. The input to the analysis was the n--2 task repetition cost for response repetitions minus the n--2 task repetition cost for response switches. The posterior distributions for mean difference and effect size of difference (Cohen's $d$) are shown in Figure \ref{fig:bayesParameter}.

\begin{figure*}
\begin{center}
\includegraphics[width =\textwidth]{Images/bayesParameter.pdf}
\caption{Bayesian posterior distributions for the parameters of mean difference and effect size of difference for n--2 task repetition cost [response repetition] minus n--2 task repetition cost [response switch]. HDI = Highest Density Interval. See text for details.}
\label{fig:bayesParameter}
\end{center}
\end{figure*}

These posterior distributions present histograms of the Bayesian posterior estimate of the true mean and effect size underlying the data we obtained. The black horizontal bar represents the 95\% Highest Density Interval (HDI); in contrast to frequentist confidence intervals, we can interpret this interval as the span of parameter values we are 95\% certain the true underlying parameter lies within. The mean difference in n--2 task repetition costs for response repetitions and response switches is estimated to be -37ms; the HDI does not cross zero, so we can be confident that there is a difference between response repetitions and switches. Note, though, that the effect size of this difference is in the small range. For hypothesis testing (i.e., assessing whether episodic retrieval does impact the n--2 repetition cost or not), this is less relevant, but it is important to note if we wish to explore \emph{how much} episodic retrieval might affect n--2 repetition costs.

\subsection{Accuracy}
Accuracy analysis showed no significant effect of task sequence [$F$(1, 75) = 3.36, $p$=.07, $\eta_G^2$ = .006]; the Bayes factor for this main effect was $BF_{10}$ = 0.618, which provides only anecdotal support for the null. The main effect of response repetition was significant [$F$(1, 75) = 12.17, $p$<.001, $\eta_G^2$ = .019], suggestive of better accuracy for response repetitions (96.28\%) than for response switches (95.41\%). The Bayes factor was $BF_{10}$ = 29.66, which provides strong support for the alternative. The interaction was not significant [$F$(1, 75) = 1.32, $p$=.25, $\eta_G^2$ = .003]; the Bayes factor was $BF_{10}$ = 0.238, which provides moderate support for the null hypothesis.

@@

For clarification, note that we have not provided evidence that episodic retrieval can explain the n--2 task repetition cost entirely, but rather that it reduces the cost. Indeed, the n--2 task repetition cost was still statistically significant even when the trial parameters matched across n--2 task repetitions (i.e., n--2 response repetitions). Therefore, our findings do not provide evidence against the inhibitory explanation of these costs. Rather, we have shown that these costs can be reduced with successful episodic retrieval. As such, researchers should be cognisant of the potential contribution of episodic retrieval mismatches inflating estimates of n--2 task repetition costs when wishing to use this effect for measuring inhibition.

Our results differ to those reported by \cite{Mayr2002}. We suggest that our modifications to Mayr's original design improved the sensitivity of the paradigm to be able to detect potential episodic retrieval effects on n--2 task repetitions. The modifications were made to enhance the magnitude of n--2 task repetition costs, so that modulation of this cost with response repetitions could be more easily detected. Specifically, removing the possibility of immediate task repetitions likely enhanced the n--2 task repetition cost as it has been shown that allowing immediate repetitions reduces this cost \citep{Philipp2006}. We also used the shortest RCI used by Mayr (150ms), as it is a consistent finding that this increases the n--2 repetition cost \cite{Gade2005, Grange2009, Mayr2000, Mayr2002}. Any one of these modifications could explain the difference in results between this study and that of Mayr (2002). Future research should aim to examine the potential role for episodic retrieval influencing n--2 task repetition costs by providing further replications to this study \citep{OpenScienceCollaboration2015}.
